---
title: "House Prices"
output: html_document
---

#Libraries
```{r}
library(knitr)
library(readr)
library(ggplot2)
library(gridExtra)
library(ggrepel)
library(scales)
library(corrplot)
```

#Import data
```{r}
train <- read.csv('train.csv', stringsAsFactors = FALSE)
test <- read.csv('test.csv', stringsAsFactors = FALSE)
```

#Let's take a quick look at the sales prices 
```{r}
ggplot(data = train, aes(x = SalePrice)) +
  geom_histogram(fill = 'blue', binwidth = 10000) +
  scale_x_continuous(breaks= seq(0, 800000, by=100000), labels = comma)

```
The sales data is right skewed like we thought since fewer people can afford the more expensive houses. 

#Before we get too far in lets first establish in our mind a baseline of which variables will be most important in determining sales price. We are going to check only the numeric variables for now and compare their correlation with sales price. 
```{r}
numeric_vars <- which(sapply(train, is.numeric))
train_numeric <- train[,numeric_vars]

#get correlations of all numeric variables
cor_numeric <- cor(train_numeric, use = "pairwise.complete.obs")

#sort on decreasing correlations
cor_sorted <- as.matrix(sort(cor_numeric[,'SalePrice'], decreasing = TRUE))

#select only high correlations
cor_numeric_high <- names(which(apply(cor_sorted, 1, function(x) abs(x)>0.5)))
cor_numeric <- cor_numeric[cor_numeric_high,cor_numeric_high]

corrplot.mixed(cor_numeric, tl.col="black", tl.pos = "lt")
```
There's a lot of multicollinearity stuck in there, but the main takeaways should be that the two most correlated variables are overall quality and above grade living area. 


Now let's get to filling in missing data.

#Merge train and test sets to fill in missing data all at once.
```{r}
temp_train <- train[,-81]
full <- rbind(temp_train, test)
```

#Looking at missing data and seeing how bad it is
```{r}
NAcol <- which(colSums(is.na(full)) > 0)
sort(colSums(sapply(full[NAcol], is.na)), decreasing = TRUE)
```
There's a lot of columns with missing data so we need to be smart with how we fill this in. There's also not that much data, so if we just start lopping rows off we'll lose too much data.

We are going to start by filling in data that has the most missing and go in that order. We are also going to convert character variables to factors while we are here

```{r}
#PoolQC
full$PoolQC[is.na(full$PoolQC)] <- 'None'
full$PoolQC <- as.factor(full$PoolQC)

summary(full$PoolQC)
#since pools with n/a just don't have pools
```

```{r}
#MiscFeature
full$MiscFeature[is.na(full$MiscFeature)] <- 'None'
full$MiscFeature <- as.factor(full$MiscFeature)

summary(full$MiscFeature)
#same thing with Misc Feature
```

```{r}
#Alley
full$Alley[is.na(full$Alley)] <- 'No alley access'
full$Alley <- as.factor(full$Alley)

summary(full$Alley)

#these just don't have alleys
```

```{r}
#Fence
full$Fence[is.na(full$Fence)] <- 'No fence'
full$Fence <- as.factor(full$Fence)

table(full$Fence)

```

```{r}
#FireplaceQu
full$FireplaceQu[is.na(full$FireplaceQu)] <- 'No fireplace'
full$FireplaceQu <- as.factor(full$FireplaceQu)

summary(full$FireplaceQu)
```

```{r}
#Lot Frontage
sum(is.na(full$LotFrontage))
#486 na values. We are going to fill these in with the median lot frontage values of the corresponding neighborhood

ggplot(full[!is.na(full$LotFrontage),], 
       aes(x = as.factor(Neighborhood), 
           y = LotFrontage)) +
  geom_bar(stat = 'summary', fun.y = 'median', fill = 'blue') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

for(i in 1:nrow(full)) {
  if(is.na(full$LotFrontage[i])){
    full$LotFrontage[i] <- as.integer(median(full$LotFrontage[full$Neighborhood == full$Neighborhood[i]], na.rm = TRUE))
  }
}
```

Also going to convert the other lot variables here as well to factors if necessary
```{r}
full$LotShape <- as.factor(full$LotShape)
full$LotConfig <- as.factor(full$LotConfig)
```

#Garage Variables
Now we're going to take a look at the garage variables. 

First we're going to replace the missing garage year built with the year the house was built
```{r}
full$GarageYrBlt[is.na(full$GarageYrBlt)] <- full$YearBuilt[is.na(full$GarageYrBlt)]
```

There is a problem. There are 157 na's for garage type, but 159 for the other three garage variables. That means there are 2 rows that are missing data that we need to manually check.
```{r}
kable(full[!is.na(full$GarageType) & is.na(full$GarageFinish), c('GarageCars', 'GarageArea', 'GarageType', 'GarageCond', 'GarageQual', 'GarageFinish')])
```
2127 Does seem to have a garage, but 2577 does not. To fix 2127, we will replace the 3 na's with the mode of each variable

```{r}
full$GarageCond[2127] <- names(sort(-table(full$GarageCond)))[1]
full$GarageQual[2127] <- names(sort(-table(full$GarageQual)))[1]
full$GarageFinish[2127] <- names(sort(-table(full$GarageFinish)))[1]
```

For 2577, it seems the problem is that the garage is detached, which is why the other variables say the house has no garage. 
So we'll just fix that manually
```{r}
full$GarageCars[2577] <- 0
full$GarageArea[2577] <- 0
full$GarageType[2577] <- NA
```


Now we check to make sure there are only 158 NA's for character variables

```{r}
length(which(is.na(full$GarageType) & is.na(full$GarageFinish) & is.na(full$GarageCond) & is.na(full$GarageQual)))
```
From here we clean up the rest of the garage variables












#
```{r}


```